---
title: "Introduction"
linktitle: "M0: Getting started"
menu:
  content:
    parent: Module Content
    weight: 1
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

This introduction module is a time for us to: 1) discuss the course; 2) get set up for future data work; and 3) learn/refresh some basic data management and analysis skills using R, Git, and GitHub. We'll also introduce the idea of causal inference and define the treatment effect estimands that will be of central interest throughout the course.

## Readings and other links

- Review the [syllabus](/syllabus/), [schedule](/schedule/), [content](/content/), and [assignments](/assignment/) pages for this class...just to get a feel for the site and how to navigate all of the information.
- <i class="fas fa-book"></i> Materials we'll use throughout this module:
    - Lesson 2 from [Data Science for Economists](https://github.com/uo-ec607/lectures). This is part of a course from [Grant McDermott](https://grantmcdermott.com/) with a ton of great online resources.
    - [R for Data Science](https://r4ds.had.co.nz/)
- <i class="fa fa-database"></i> Data for this module:
    - Data from [Gapminder](https://www.gapminder.org/)
    - [Medicare Advantage](https://github.com/imccart/Medicare-Advantage) repository


## Slides

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/00-introduction.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/00-introduction.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/00-introduction.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

