---
title: "Hospital Pricing and Selection on Observables"
linktitle: "M1: Selection and Pricing"
menu:
  content:
    parent: Module Content
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In this module, we'll introduce the idea of "selection on observables" and the different ways to exploit that idea to make casual statements. We'll do this in the context of hospital pricing, the research question being whether and to what extent hospitals receiving a financial penalty also raise their prices.

## Readings and other links

Links to papers are listed alongside the full reference. PDFs of each paper are also available on **Canvas**.

- <i class="fas fa-book"></i> Required readings for this module:
    - Chapter 5 of [Causal Inference: The Mixtape](https://mixtape.scunning.com/)
    - Chapter 14 of [The Effect: An Introduction to Research Design and Causality](https://theeffectbook.net/)
- <i class="fas fa-external-link-square-alt"></i> Supplemental information and readings:
    - Chapters 1-2, and 4 of [Causal Inference: The Mixtape](https://mixtape.scunning.com/)
    - Chapters 1-5, 10, and 13 of [The Effect: An Introduction to Research Design and Causality](https://theeffectbook.net/)
    - Chapters 2-3 of [@angrist2009]
    - [@darden2018]
    - [@cooper2019]    
- <i class="fa fa-database"></i> Data for this module:
    - [Hospital Cost Report Information System (HCRIS)](https://github.com/imccart/HCRIS) repository
    - See also a similar repository [here](https://github.com/asacarny/hospital-cost-reports) from [Adam Sacarny](http://sacarny.com/)
    

## Slides

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/01-hospital-pricing/01-hospital-pricing.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/01-hospital-pricing/01-hospital-pricing.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/01-hospital-pricing/01-hospital-pricing.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
