---
title: "Demand for Cigarettes and Instrumental Variables"
linktitle: "M2: Smoking and IV"
menu:
  content:
    parent: Module Content
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

The goal of this module is to understand instrumental variables as a causal identification strategy. We'll do this in the context of smoking and cigarette prices. Effectively, we want to estimate a demand curve for cigarettes, accounting for the fact that price is an outcome of the demand function and therefore endogenous.


## Readings and other links

Links to papers are listed alongside the full reference. PDFs of each paper are also available on **Canvas**.

- <i class="fas fa-book"></i> Required readings for this module:
    - Chapter 7 of [Causal Inference: The Mixtape](https://mixtape.scunning.com/)
    - Chapter 19 of [The Effect: An Introduction to Research Design and Causality](https://theeffectbook.net/)
- <i class="fas fa-external-link-square-alt"></i> Supplemental information and readings:
    - Chapter 4 of [@angrist2009]
    - [@gruber2001]
    - [@ross2003]    
- <i class="fa fa-database"></i> Data for this module:
    - [CDC Tax Burden on Tobacco](https://github.com/imccart/CDC-Tobacco)


## Slides

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::


<center>

```{r}
knitr::include_url("https://imccart.github.io/Econ470-content/02-smoking.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ470-content/02-smoking.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/Econ470-content/02-smoking.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

